Spin canonical divisors of log stacky curves

### 2015-06-22 stacky_write_up/spin_cring.tex
added subsections
modify def admissible, reword base cases

Let $R'$ be the canonical ring associated to $\sx'$. Say $(\sx',J)$,
{\bf admissible} if the following three conditions hold.  \todo{Peter: We should make the definition of admissibility be a condition for the triple: $(\sx',\sx,J)$.}

\begin{enumerate}
	\item[(Ad-i)] Suppose for all $i \in J$, there exists $y_{i,e_i'} 
		\in R'$ so that $R'$ admits a presentation
		\begin{align*}
			R' \cong \left( k[x] \otimes k[y_{i,e_i'}]_{i \in J} \right)/I'
		\end{align*}
		so that for all $i \in J$ we have $\deg y_{e_i'} = e_i'$ and $-ord_{
		Q_i}(y_{i,e_i'}) = \frac{e_i'-1}{2}$.
	\item[(Ad-ii)] For all $i \in J$, any generator $z \neq y_{i,e_i'}$
		of $R'$ satisfies
		\begin{align*}
			\frac{- ord_{Q_i}(z)}{\deg z} < \subhalf {e_i'}.
		\end{align*}
	\item[(Ad-iii)] For all $i \in J$ we have
		\begin{align*}
			\deg \lfloor e_i L \rfloor \geq 2g - 1 + \max_{d \geq 0} \# S_{\sigma, J}(i, d)
		\end{align*}
		\todo{Check the 2g - 1, in particular, David seems to think we are usually 1 off and possibly 2 off when g = 1. I have a feeling this is a mistake, but don't understand why.} 
		where
		\begin{align*}
			S_{\sigma, J}(i, d) := \{j \in J : j \neq i \text{ and } e_j'+2d
			\mid e_i - e_j'\}
		\end{align*}
\end{enumerate}
\end{defn}

@@

\section{High genus}
Aaron will write amazing things here.

@@

\begin{proof}
For each case, computations using a combination of Riemann-Roch and
comparing pole orders at each ramification point $P_i$ gives the
generator and relation degrees.

@@

Note that (Ad-i) always holds.
In each case we can also pick a set of generators such that
(Ad-ii) holds. \todo{justification for these}

@@

Thus, we have admissibility of $(\sx', J)$ in each of these cases.

Finally, each case also satisfies the property that $in_\prec(I')$ is
minimally generated by products of two monomials.
\todo{prove}
\end{proof}

@@

\section{Acknowledgements}
We are grateful to David Zureick-Brown for introducing us to this
field of study, providing incredibly helpful guidance, and being an
excellent project mentor. We also thank Ken Ono and the Emory University
Number Theory REU for arranging our project and providing a great
environment for mathematical learning and collaboration. Finally, we
gratefully acknowledge that our research was financially supported by
NSF Grant Award Number 1250467 via the Emory University Number Theory REU.
We deeply appreciate all of the support that has made our work possible.

>>>>

Let $R'$ be the canonical ring associated to $\sx'$. Define $(\sx',J)$
to be {\bf admissible} if the $R'$ admits a presentation

\begin{align*}
	R' \cong \left( k[x_1, \ldots, x_m] \otimes k[y_{i,e_i'}]_{i \in J} \right)/I'
\end{align*}

\noindent
with $y_{i,e_i'} \in R'$ for each $i \in J$ such that the following
three conditions hold.

\todo{Peter: We should make the definition of admissibility be a 
condition for the triple: $(\sx',\sx,J)$.}

\begin{enumerate}
	\item[(Ad-i)] For all $i \in J$, $\deg y_{e_i'} = e_i'$ and $-ord_{
		Q_i}(y_{i,e_i'}) = \frac{e_i'-1}{2}$.
	\item[(Ad-ii)] For all $i \in J$, any generator $z \neq y_{i,e_i'}$
		of $R'$ satisfies
		\begin{align*}
			\frac{- ord_{Q_i}(z)}{\deg z} < \subhalf {e_i'}.
		\end{align*}
	\item[(Ad-iii)] For all $i \in J$ we have
		\begin{align*}
			\deg \lfloor e_i L \rfloor \geq 2g - 1 + \max_{d \geq 0} \# S_{\sigma, J}(i, d)
		\end{align*}
		\todo{Check the 2g - 1, in particular, David seems to think we are usually 1 off and possibly 2 off when g = 1. I have a feeling this is a mistake, but don't understand why.} 
		where
		\begin{align*}
			S_{\sigma, J}(i, d) := \{j \in J : j \neq i \text{ and } e_j'+2d
			\mid e_i - e_j'\}
		\end{align*}
\end{enumerate}
\end{defn}

@@

\ssec{Genus 1 base cases}

\ssec{Main Theorem for Genus 1}

\section{High genus}

\ssec{Inductive Theorem: Adding points for high genus}

\ssec{Bounds on Generators and Relations in high genus}

\ssec{Main theorem for high genus}

@@

\begin{example}
Here we demonstrate, in detail, that case (b) ($\sigma_2 =
(0; 3, 5, 9; 0), J_2 = \{3\}$) satisfies the conditions.
\end{example}

\begin{proof}
For these cases, we can always find a presentation satisfying (Ad-i).
Furthermore, we can verify that these base cases satisfy the
remaining conditions using computations of Riemann-Roch and pole
orders similar to those in the given example.

@@

@@

All that remains to be shown is that these cases satisfy
(Ad-ii) and that $in_\prec(I')$ is minimally generated by
products of two monomials. The procedure for verifying these
are similar to those for the given example. Below, we
give a table for the explicit generators and initial ideals.
\todo{make table}
\end{proof}

@@

\section{Acknowledgments}
We are grateful to David Zureick-Brown for introducing us to this
field of study, providing incredibly helpful guidance, and being an
excellent project mentor. We also thank Ken Ono and the Emory University
Number Theory REU for arranging our project and providing a great
environment for mathematical learning and collaboration. Finally, we
gratefully acknowledge that our research was financially supported by
NSF Grant Award Number 1250467 via the Emory University Number Theory REU.
We deeply appreciate all of the support that has made our work possible.
